Evolutionary Computing and Machine Learning

### 2018-09-01 AI/EC.tex

\subsection{Related Work}

@@

\includepdf[link=true,pages=-,fitpaper]{./papers/Population-Based-Training-of-Neural-Networks.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}
%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

>>>>

\subsection{Related Work}
\paragraph{Bayesian optimisation framework}
\paragraph{Main thoughts of PBT for training}A misture way: Parameters are more likely to be trained(partially) in standard way, while the hyperparameters are evolved(relatively slowly).

\subsection{Population Based Training}
\paragraph{Main idea}
\begin{itemize}
\item Training with a population that each member has different parameters and hyper parameters.
\item In each iteration, a member takes steps and offer its weights, hyperparameters and evaluation. This is the main \textbf{communication} among members.
\item Each member \textbf{\textit{exploit}} the best weights and hyperparameters among the whole polulation, then \textbf{\textit{explore}} new branches for next step.
\end{itemize}
\textbf{Remark. }Can we treat objective function as a \textbf{hyperparameter} too?\\
e.g. With the improvement of models, can we eventually decrease the size of the batches for evaluation computing?\\

\subsection{Experiments}
\subsubsection{Deep Reinforcement Learning}

\subsubsection{Machine Translation}

\section{\textit{Evolution Strategies as a Scalable Alternative to Reinforcement Learning}}
\book{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}{1}\\
\textbf{Remark. }Someone pointed out that this paper is similar to \href{https://en.wikipedia.org/wiki/Simultaneous\_perturbation\_stochastic\_approximation}{SPSA}

@@

\includepdf[link=true,pages=-,fitpaper]{./papers/Population-Based-Training-of-Neural-Networks.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}
%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}
